### 2025-07-21 decision-making.qmd
20250720 - fix

```{r}
weeklyIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n()) %>% 
  as.numeric()
```

@@

proportionZeroBracketingRate_weekly <- weeklyIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n())
```

>>>>

```{r}
weeklyIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n())
```

@@

proportionZeroBracketingRate_weekly <- weeklyIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n()) %>% 
  as.numeric()
```
